\chapter{Concept}

Hier Architekturdiagramm (mehrere Gates haben einen Endpunkt bei uns wo sie logs hinschieben koennen)

Generelles Konzept erklaeren

To be able to meet the requirements for our interactive floorplan, the events from the gate need to be logged and displayed in real-time. For this to work, there a 4 Players involved.


\section{Gates}
\label{Gates}

The gates need to capture with which device the person at the gate tried to access. Furthermore it is important 

The gate than is responsible of sending this information to our system. has to take care of sending this 

Gates kommunizieren ueber API Endpunkt mit uns, preshared token blabla

Glaube hier noch sehr abstrakt reden

\section{Backend}
\label{Backend}

The backend offers interfaces for the gates and also the frontend. For the gates it provides an interface which allows the gates to send events to, which then will be persisted as logs.
For the frontend provides routes for retrieving logs and also other results based on these.

It emits notifications once a gate event has happened together with sending information about the event for a real time frontend application.




The backend takes care of logging the events and also for providing an interface for the frontend and the gates.
This communication has to be secured...

The backend than takes care of sending this information to our elastic stack.

loggt die events von den Gates
schickt benachrichtung ueber sockets weiter an frontend

bietet frontend endpunkte an um access decisions herauszufinden

\section{Frontend}
\label{Frontend}

The frontend listens for the gate event notification sent from the backend. When an event occurs the frontend reads in the gate event informationen. With this it finds out who accessed at which gate and presents that information to the facility management. It then asks for the backend for an updated number of people behind that specific gate. It than calculates the heat in that specific an rerenders the color of that room accordingly.





